% Acknowledgement: The below resume is based on aome510's resume [1]
%
% [1]: https://github.com/aome510/resume


\documentclass[letterpaper,11pt]{article}
\usepackage{fontawesome5}
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-7pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt} ]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\linkDesc}[1]{\underline{\texttt{#1}}}

\newcommand{\resumeItem}[2]{
	\item\small{#1{: #2}} \vspace{-2pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2} \vspace{-2pt}}

\newcommand{\resumeDescItem}[1]{\item[-]\small{#1} \vspace{-2pt}}
\newcommand{\resumeDescItemNoBullet}[1]{\item[]\small{#1} \vspace{-2pt}}

\newcommand{\resumeHeading}[4]{
	\begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheading}[4]{
	\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeListStart}{\vspace{-2pt}\begin{itemize}[leftmargin=*]}
		\newcommand{\resumeListEnd}{\end{itemize}}

\renewcommand{\labelitemii}{$\circ$}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	\LARGE\textbf{Brian  Luu}
	& \faIcon{mobile-alt} (+61) 431 888 818\\
	\href{https://github.com/aome510}{\faIcon{github} nbonair}
	\href{https://www.linkedin.com/in/nbonair/}{\faIcon{linkedin} nbonair}
	& \href{mailto:lnnb.imc@gmail.com}{\faIcon{envelope} lnnb.imc@gmail.com}
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
\resumeHeading
{Deakin University}{Burwood, VIC, Australia}
{Bachelor of Computer Science }{March 19 - Jul 23}
\resumeListStart
\resumeDescItem {Specialization in Artificial Intelligence and Data Science.}
\resumeDescItem{WAM: 82/100.}
\resumeDescItem{Recipient of Deakin's International Student Scholarship.}
\resumeListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeListStart

\resumeSubheading
{Buildmat Trade}{Dandenong South, VIC, Australia}
{Data Engineer}{Jul 23 - now}
\resumeListStart
\resumeDescItem{Designed and refined a data pipeline to process semi-structured data, enabling the generation of insightful visualization reports crucial for informed business decision-making.}
\resumeDescItem{Created specialized data scrapers utilizing Python libraries, expanding the data resources by 70\% and enabling timely insights for business analysis.}
\resumeDescItem{Developed and managed a cloud-hosted PostgreSQL database using Python ORM and Amazon RDS, ensuring scalability real-time data accessibility.}
\resumeDescItem{Developed API for database services, enabling cross-functional teams to efficiently manage and utilize data.}
\resumeDescItem{Technologies implemented: Amazon RDS, SQLAlchemy ORM, FastAPI, Python, PowerBI }
\resumeListEnd

\resumeSubheading
{Applied Artificial Intelligence Institute (A2I2)}{Burwood, VIC, Australia}
{AI Engineer Intern}{March 23 - now}
\resumeListStart
\resumeDescItem{Developed a semantic search engine for expert identification, improving result accuracy by 15\% through a hybrid approach integrating Large Language Models, Graph-based Models, and Clustering Algorithms with custom datasets.}
\resumeDescItem{Launched a beta web application that identifies experts and publications based on user queries, enables expert network generation from specified domains, long-text queries (abstract/section) and expert profiles.}
\resumeDescItem{Models and algorithms implemented: Sentence-BERT, UMAP, HDBSCAN, PageRank.}
\resumeDescItem{Framework and technologies implemented: TensorFlow, FastAPI, Neo4J, TryChroma, NetworkX.}
\resumeListEnd

\resumeSubheading
{Department of Education and Training }{Melbourne, VIC, Australia}
{Specialist Technician}{March 23 - now}
\resumeListStart
\resumeDescItem{Configured, managed and maintained curriculum and admin networks, servers and educational smart devices.}
\resumeDescItem{Installed and managed hardware and software, introducing automation procedures that reduced administrative workload by over 25\%.}
\resumeDescItem{Managed the Windows Server 2016 environment, MDM services, and Microsoft Intune Services, ensuring 99.9\% uptime and secure network operations}
\resumeListEnd

\resumeSubheading
{Vega Corporation, }{Hanoi, Vietnam}
{Software Engineer Intern}{June 18 - December 18}
\resumeListStart
\resumeDescItem{Contributed to the development and maintenance of features on a music streaming web application.}
\resumeDescItem{Partnered with the testing team to validate product features, leading to a 20\% reduction in bugs and errors.}
\resumeDescItem{Technologies implemented: React, Node.Js, MongoDB.}

\resumeListEnd

\resumeListEnd

%-----------PROJECTS-----------------
\section{Projects}
\resumeListStart
\resumeItem{\href{https://github.com/nbonair/Text-Captcha}{\linkDesc{Breaking Captcha}}}{A web tool enabling users to solve diverse CAPTCHA types with Computer Vision models, showcasing a practical application of AI in bypassing security challenges.}
\vspace{-5pt}
\resumeItem{\href{}{\linkDesc{RecycleNet}}}{A Streamlit application that employs a fine-tuned Vision Transformer model to classify recyclables according to Victoria's regulations, achieving 92\% accuracy on the TrashNet dataset. }
\vspace{-5pt}
\vspace{-5pt}
\resumeListEnd

% --------SKILLS------------
\section{Skills}
\resumeListStart
\resumeSubItem{Languages}{Python, Javascript, C/C++}
\resumeSubItem{Frameworks:}{TensorFlow, PyTorch, ORM, FastAPI, Flask, React.Js, Express.Js}
\resumeSubItem{Tools}{Git, AWS, PostgreSQL, Docker, PowerBI, Postman}
\resumeListEnd

%-------------------------------------------
\end{document}